The Bug Catalog of the Maven Ecosystem

### 2014-02-21 docs/msr.tex
fina changes

\maketitle
\begin{abstract}
Examining software ecosystems can provide the research community
with data regarding artifacts, processes, and communities.
We present a dataset obtained from the Maven central repository
ecosystem (approximately 265{\sc gb} of data) by statically analyzing
the repository to detect potential software bugs.
For our analysis we used FindBugs, a tool that examines Java
bytecode to detect numerous types of bugs.
The dataset contains the metrics results that FindBugs reports for
every project version (a {\sc jar}) included in the ecosystem. For every
version we also stored specific metadata such as the {\sc jar}'s
size, its dependencies and others. Our dataset can be used to produce
interesting research results, as we show in specific examples.
\end{abstract}

@@

\terms{Static Analysis, Software Ecosystems}

\keywords{Maven Repository, FindBugs, Software Bugs}

@@

In this paper we present: a) the construction process to obtain the
collection of the metrics results that the FindBugs tool produces 
for every project version of the repository (115,214 {\sc jar}s)
and b) how researchers can use the dataset and produce
meaningful results.

@@

When the processing was completed, we ran some tests
to check the validity of the results.
A common issue that we discovered was the out-of-memory
crashes of Findbugs, which demanded the repetition of the process
for the corresponding {\sc jar}s, with the appropriate
settings in the Java Runtime Environment ({\sc jre}).
%The sanitisation process was consisted of four iterations,
%until all our scripts indicate that our data was correct.

@@

\begin{table}[t]
\centering
\scalebox{0.80}{
\begin{tabular}{l p{16em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding misting a way that is particularly different from the other bug sakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalization (i18n) & Indicates the use of non-localized methods. \\
Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usage allocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}}
\caption{Bug categorization according to FindBugs.}
\label{tbl:bug-cat}
\end{table}

@@

Together with our dataset, we have also created a series of
scripts to exhibit how the dataset can be used
to capture correlations regarding
the evolution of software bugs.
First, based on the dataset we produced some metadata
that contained the number of
bugs per category in each project version. Based
on these metadata we estimated the relation between
bugs and time (see Table~\ref{tbl:bugsperversion}).
Specifically, we calculated the Spearman correlations between the defects
count and the ordinal version number across all projects.
The zero tendency that can be seen on Table~\ref{tbl:bugsperversion}
applies to all versions of all projects together.

@@

Finally, Figure~\ref{fig:corrplot} presents the pairwise correlations
between all bug categories. To establish these correlations,
we calculated the correlations between the number of
distinct bugs that appeared in a project throughout its lifetime.

@@

A disadvantage of our dataset is that as projects evolve
the dataset gets older. Also, even if we checked for
new versions before data cleaning and before
the results collection, we did not checked for new
projects added during this time frame.

>>>>

\maketitle
\begin{abstract}
Examining software ecosystems can provide the research community
with data regarding artifacts, processes, and communities.
We present a dataset obtained from the Maven central repository
ecosystem (approximately 265{\sc gb} of data) by statically analyzing
the repository to detect potential software bugs.
For our analysis we used {\it FindBugs}, a tool that examines Java
bytecode to detect numerous types of bugs.
The dataset contains the metrics results that FindBugs reports for
every project version (a {\sc jar}) included in the ecosystem. For every
version we also stored specific metadata such as the {\sc jar}'s
size, its dependencies and others. Our dataset can be used to produce
interesting research results, as we show in specific examples.
\end{abstract}

@@

\terms{Static Analysis, Software Ecosystems.}

\keywords{Maven Repository, FindBugs, Software Bugs.}

@@

In this paper we present: a) the construction process to obtain the
collection of the metrics results that the FindBugs tool produces 
for every project version of the repository (115,214 {\sc jar}s),
b) our dataset
and c) how researchers can use the dataset and produce
meaningful results.

@@

When the data collection was completed, we ran some tests
to check the validity of the results.
A common issue that we discovered was the out-of-memory
crashes of Findbugs, which demanded the repetition of the process
for the corresponding {\sc jar}s, with the appropriate
settings in the Java Runtime Environment ({\sc jre}).
%The sanitisation process was consisted of four iterations,
%until all our scripts indicate that our data was correct.

@@

\begin{table}[t]
\centering
\scalebox{0.79}{
\begin{tabular}{l p{16em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding misting a way that is particularly different from the other bug sakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalization (i18n) & Indicates the use of non-localized methods. \\
Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usage allocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}}
\caption{Bug categorization according to FindBugs.}
\label{tbl:bug-cat}
\end{table}

@@

Furthermore, we have created a series of
scripts to exhibit how the dataset can be used
to capture correlations regarding
the evolution of software bugs.
First, based on the dataset we produced some metadata
that contained the number of
bugs per category in each project version. Based
on these metadata we estimated the relation between
bugs and time (see Table~\ref{tbl:bugsperversion}).
Specifically, we calculated the Spearman correlations between the defects
count and the ordinal version number across all projects.
The zero tendency that can be seen on Table~\ref{tbl:bugsperversion}
applies to all versions of all projects together.

@@

Figure~\ref{fig:corrplot} presents the pairwise correlations
between all bug categories. To establish these correlations,
we calculated the correlations between the number of
distinct bugs that appeared in a project throughout its lifetime.

@@

A disadvantage of our dataset is that as projects evolve
the dataset gets older. Also, even if we checked for
new project versions that could have been added
to the repository after the data cleaning and before
the results collection, we did not checked for new
projects added during this time frame.
